The \dealii{} Library, Version 9.2

### 2020-06-01 9.2/paper.tex
add a section about large scale Stokes

By replacing the collective communications during set up and removing the arrays
that contain information for each process (enabled by the application of consensus
algorithms and other modifications---a full list of modifications leading to this
improvement can be found online), we were able to significantly
improve the set up
time for large-scale simulations and to solve a Poisson problem with multigrid
with \num{2.1e12} unknowns.
Figure~\ref{fig:init_costs} compares timings of simulations of various problem
sizes (including set up) on 49,152 MPI ranks using a matrix-free
solver~\cite{KronbichlerKormann2019,KronbichlerWall2018}; this solver uses discontinuous elements of
degree $5$ in a geometric multigrid (GMG) scheme. The comparison between the previous release 9.1
and the current release 9.2 shows that while the scaling for the V-cycle had been
very good before, many initialization routines have been considerably
improved, especially the enumeration of unknowns on the multigrid levels and
the setup of the multigrid transfer.

@@

\todo[inline]{Timo: Do you want to say something about that the new code has been also applied to solve problems with adaptively refined
  meshes with more than \num{4e9} unknowns?}

\todo[inline]{Timo says: We did solve adaptive problems with more than
  4B unknowns before, but some were broken for a while during this
  release stage due to the consensus algorithms. But we did not test
  systems or block vectors before. But we should not make it sound too
  negative.}

\todo[inline]{Wolfgang says: Should we just not mention any of this at
  all? The section stands well on its own.}

>>>>

By replacing the collective communications during set up and removing the arrays
that contain information for each process (enabled by the application of consensus
algorithms and other modifications---a full list of modifications leading to this
improvement can be found online), we were able to significantly
improve the set up
time for large-scale simulations and to solve a Poisson problem with multigrid
with \num{2.1e12} unknowns.
\todo[inline]{the figure only shows 2e11 unknowns. Is this a typo? If not, do we have a reference?}
Figure~\ref{fig:init_costs} compares timings of simulations of various problem
sizes (including set up) on 49,152 MPI ranks using a matrix-free
solver~\cite{KronbichlerKormann2019,KronbichlerWall2018}; this solver uses discontinuous elements of
degree $5$ in a geometric multigrid (GMG) scheme. The comparison between the previous release 9.1
and the current release 9.2 shows that while the scaling for the V-cycle had been
very good before, many initialization routines have been considerably
improved, especially the enumeration of unknowns on the multigrid levels and
the setup of the multigrid transfer.

@@

As part of this effort, we ran benchmarks on the TACC Frontera system, where we were able to apply the matrix-free geometric multigrid framework to a variable viscosity Stokes system and achieved weak and strong scaling up to 114k MPI ranks with up to
\num{2.1e11} unknowns. This is likely the currently largest block system solved with \dealii{} and required various optimizations
and fixes on top of the ones mentioned above:
1) Bug fixes to concurrent point to point communications.
2) Fixes multigrid transfer with adaptive refinement and more than \num{4e9} unknowns.
3) Fixes to index sets in block indices with more than \num{4e9} unknowns.
4) Fixes to computations with more than \num{4e9} active cells.
5) Implementation of IDR(s) solvers to reduce memory overhead.
For more details, see \cite{clevenger_stokes19}.

\todo[inline]{Timo added the paragraph above. Thoughts on how much we should mention (none of this worked with 9.1)?}
